|

### 2023-06-01 manuscript/Chapter2-appendix3.Rmd
update appendix S3 figure legends

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among each predator experience level. The test is displayed on the y axis (i.e. whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience levels being compared. The results are from the model that includes the outlier."}

>>>>

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels. The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is displayed on the x axis. The pairwise comparisons between experience levels are displayed across the three panels A, B, and C. The results are from the model that includes the outlier."}
